PMV: Which formulation should you use the ISO 7730:2005 or ASHRAE 55:2020?

### 2023-08-29 Manuscript/src/sections/results.tex
paper: updated Fig 2 and 3

\subsection{\ac{db2} overview}\label{subsec:comfort-db-overview}
While the \ac{db2} contains \var{entries_db_all} data points, only \var{entries_db_used} entries met the inclusion criteria listed in the Methodology section.
The distribution of the six input variables used to calculate the PMV indices is visualized in Figure~\ref{fig:dist_input_data}.
The 2.5th, 50th (median), and 97.5th percentiles are shown in blue.
% todo: remove the gridlines or marker them very short; remove outliers or make the line very thin; keep one decimal for clo values; remove decimal point for RH; annotation font should be the same as the label and same size, change only the color; You can use black or blue (HEX: 003262, RGB (0, 50, 98)) for the chart; one decimal for met not two; the chart is a bit dense of information
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/dist_input_data}
    \caption{Distribution of the input variables used to calculate the \ac{pmv} and \ac{pmv-ce} values.
    The text in blue is showing the 2.5th, 50th (median), and 97.5th percentiles.
    The data are shown using boxen plots (letter-value plots).
    They depict the median as the center-line and each successive level outward contains half of the remaining data.}
    \label{fig:dist_input_data}
\end{figure*}
The input data distributions are far from uniformity (equal density) across the Standards' applicability ranges.
We were not able to determine the accuracy of the \ac{pmv} and \ac{pmv-ce} formulations for inputs that were lower than the 2.5th and 97.5th percentiles, since we only had a limited number of data points beyond those values.
For example, only 2.5\% of the available dataset had a \ac{tdb} $\leq$ than \var{ta_95_perc_min}, this may consequently be an issue since both thermal comfort Standards' applicability limits extend to \qty{10}{\celsius}.
This can be explained by the fact that only a few buildings in the world operate at \ac{tdb} lower than this value.
This is because an indoor \ac{tdb} lower than \var{ta_95_perc_min} would be deemed to be unsatisfactory by a great number of occupants~\cite{iso7730}.
This lack of data in the \ac{db2} is particularly relevant for \ac{v}.
The \ac{pmv} and \ac{pmv-ce} only differ when the value of \ac{v} $\geq$ \qty{0.1}{\m\per\s}, however, the median value in the \ac{db2} was \qty{0.08}{\m\per\s} suggesting that most of the data points were collected in buildings with low air movement.
Consequently, we could not reliably test the accuracy of the \ac{pmv} formulations for values of \ac{v} $\geq$ \var{v_95_perc_max}.

Figure~\ref{fig:dist_other_data} shows the distribution of age, height, weight, and running mean outdoor temperature grouped by sex.
Less than half (\num{23300}) of the total entries have information about the participant's sex and are almost equally distributed among males \qty{52}{\percent} and females.
Men were significantly heavier and taller than females.
Ages are not normally distributed, the same is true for the running mean outdoor temperature.
About half of the participants (\qty{52}{\percent}) were aged between \num{20} and \num{35} years old, and only \qty{2.5}{\percent} were older than 60.
This limits our analysis to young adults and does not allow us to determine the accuracy of the \ac{pmv} and \ac{pmv-ce} models in predicting thermal sensation for children or older adults.
The \ac{db2} does not contain information about the health status of the participants.
Approximately \qty{56}{\percent} of the running mean outdoor temperature values where between \qtyrange{10}{25}{\celsius}.
% todo: check that the colours are distinguishable for color blind and change them since I am using the same color palette to differentiate PMV and PMVCE; same comments as previous chart; use a boxen plot and have 4 for men and 4 for women. Tormt is missing the unit; age unot should be year. This figure can be merged with figure 2 because it is a visualization of the database. I would use blue (HEX: 003262, RGB (0, 50, 98)) and gold (HEX: FDB515, RGB (253, 181, 21)) as color because blue and green could be confounded by colorblind people. To be more consisten in the paper, I would use the letter value plots for this and the figure in section 3.3.2
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/dist_other_data}
    \caption{Distribution of age, height, weight, and running mean outdoor temperature.
    The data are grouped by sex.
    The text in blue is showing the 2.5th, 50th (median), and 97.5th percentiles.}
    \label{fig:dist_other_data}
\end{figure*}
The percentage of \ac{tpv} grouped by each \ac{tsv} is shown on the left side of Figure~\ref{fig:bar_plot_tp_by_ts}.
Only \var{entries_with_tp} entries had information about both \ac{tsv} and \ac{tpv}.
Thus, on the right, we show a bar chart depicting the distribution of all the \ac{tsv} votes, we analyzed in the paper.
The \ac{tsv} is unbalanced. 
Approximately \var{perc_tsv_neutral} of all the entries have a \ac{tsv} of `Neutral'.
While less than \var{perc_tsv_hot} of the total sample of participants reported to be either `Hot' or `Cold'.
% todo I really do not like this color, they are misleading. If someone want to be "warmer", then it should be shown as blue. I suggest to use the color pallet (figure 3) that Micheal used in the BCA paper. 
% todo TSV report words not numbers.
% todo TSV chart the color here should not match the one on the thermal preference scale given that it is a different question. For example, a TSV=3 is red, like people that wants to be warmer, meaning that they are cold. Even with the inversion of the color palette, we cannot imply that TSV=3 mease wanted to be cooler. What about TSV=1, maybe people want no changer or cooler or warmer. Difficult to assume. Better to use two independet color schemes. 
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bar_plot_tp_by_ts}
    \caption{The left Figure shows the percentage of \ac{tpv} for each thermal sensation vote.
    The numbers on the right side of each bar show the number of points for each \ac{tsv}.
    The right figure shows the total number of data points grouped by \ac{tsv}.
    Each bin in the right figure has more data points than in the left figure since less data on \ac{tpv} were available.}
    \label{fig:bar_plot_tp_by_ts}
\end{figure*}

>>>>

\subsection{\ac{db2} overview}\label{subsec:comfort-db-overview}
While the \ac{db2} contains \var{entries_db_all} data points, only \var{entries_db_used} entries met the inclusion criteria listed in the Methodology section.
The distribution of the six input variables used to calculate the PMV indices is visualized in Figure~\ref{fig:dist_input_data}.
The 2.5th, 50th (median), and 97.5th percentiles are shown in blue.
% TODO:
%  remove the gridlines or marker them very short
%  the chart is a bit dense of information
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/dist_input_data}
    \caption{Distribution of the input variables used to calculate the \ac{pmv} and \ac{pmv-ce} values.
    The text in blue is showing the 2.5th, 50th (median), and 97.5th percentiles.
    The data are shown using boxen plots (letter-value plots).
    They depict the median as the center-line and each successive level outward contains half of the remaining data.}
    \label{fig:dist_input_data}
\end{figure*}
The input data distributions are far from uniformity (equal density) across the Standards' applicability ranges.
We were not able to determine the accuracy of the \ac{pmv} and \ac{pmv-ce} formulations for inputs that were lower than the 2.5th and 97.5th percentiles, since we only had a limited number of data points beyond those values.
For example, only 2.5\% of the available dataset had a \ac{tdb} $\leq$ than \var{ta_95_perc_min}, this may consequently be an issue since both thermal comfort Standards' applicability limits extend to \qty{10}{\celsius}.
This can be explained by the fact that only a few buildings in the world operate at \ac{tdb} lower than this value.
This is because an indoor \ac{tdb} lower than \var{ta_95_perc_min} would be deemed to be unsatisfactory by a great number of occupants~\cite{iso7730}.
This lack of data in the \ac{db2} is particularly relevant for \ac{v}.
The \ac{pmv} and \ac{pmv-ce} only differ when the value of \ac{v} $\geq$ \qty{0.1}{\m\per\s}, however, the median value in the \ac{db2} was \qty{0.08}{\m\per\s} suggesting that most of the data points were collected in buildings with low air movement.
Consequently, we could not reliably test the accuracy of the \ac{pmv} formulations for values of \ac{v} $\geq$ \var{v_95_perc_max}.

Figure~\ref{fig:dist_other_data} shows the distribution of age, height, weight, and running mean outdoor temperature.
Less than half (\num{23300}) of the total entries have information about the participant's sex and are almost equally distributed among males \qty{52}{\percent} and females.
Ages are not normally distributed, the same is true for the running mean outdoor temperature.
About half of the participants (\qty{52}{\percent}) were aged between \num{20} and \num{35} years old, and only \qty{2.5}{\percent} were older than 60.
This limits our analysis to young adults and does not allow us to determine the accuracy of the \ac{pmv} and \ac{pmv-ce} models in predicting thermal sensation for children or older adults.
The \ac{db2} does not contain information about the health status of the participants.
Approximately \qty{56}{\percent} of the running mean outdoor temperature values where between \qtyrange{10}{25}{\celsius}.
% todo:
%  I merged men and women since not considering sex difference in the paper.
%  This figure can be merged with figure 2 because it is a visualization of the database.
%  To be more consisten in the paper, I would use the letter value plots for this and the figure in section 3.3.2
% remove the gridlines or marker them very short;
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/dist_other_data}
    \caption{Distribution of age, height, weight, and running mean outdoor temperature.
    The data are grouped by sex.
    The text in blue is showing the 2.5th, 50th (median), and 97.5th percentiles.}
    \label{fig:dist_other_data}
\end{figure*}
The percentage of \ac{tpv} grouped by each \ac{tsv} is shown on the left side of Figure~\ref{fig:bar_plot_tp_by_ts}.
Only \var{entries_with_tp} entries had information about both \ac{tsv} and \ac{tpv}.
Thus, on the right, we show a bar chart depicting the distribution of all the \ac{tsv} votes, we analyzed in the paper.
The \ac{tsv} is unbalanced. 
Approximately \var{perc_tsv_neutral} of all the entries have a \ac{tsv} of `Neutral'.
While less than \var{perc_tsv_hot} of the total sample of participants reported to be either `Hot' or `Cold'.
% todo I really do not like this color, they are misleading. If someone want to be "warmer", then it should be shown as blue. I suggest to use the color pallet (figure 3) that Micheal used in the BCA paper. 
% todo TSV report words not numbers.
% todo TSV chart the color here should not match the one on the thermal preference scale given that it is a different question. For example, a TSV=3 is red, like people that wants to be warmer, meaning that they are cold. Even with the inversion of the color palette, we cannot imply that TSV=3 mease wanted to be cooler. What about TSV=1, maybe people want no changer or cooler or warmer. Difficult to assume. Better to use two independet color schemes. 
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bar_plot_tp_by_ts}
    \caption{The left Figure shows the percentage of \ac{tpv} for each thermal sensation vote.
    The numbers on the right side of each bar show the number of points for each \ac{tsv}.
    The right figure shows the total number of data points grouped by \ac{tsv}.
    Each bin in the right figure has more data points than in the left figure since less data on \ac{tpv} were available.}
    \label{fig:bar_plot_tp_by_ts}
\end{figure*}
